---
title: "Ask"
author: "JK"
date: "11/9/2021"
#output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

These questions will guide your analysis:

1. What are some trends in smart device usage?
2. How could these trends apply to Bellabeat customers?
3. How could these trends help influence Bellabeat marketing strategy?

You will produce a report with the following deliverables:

1.  A clear summary of the business task
2.  A description of all data sources used
3.  Documentation of any cleaning or manipulation of data
4.  A summary of your analysis
5.  Supporting visualizations and key findings
6.  Your top high-level content recommendations based on your analysis

<br/><br/><br/><br/><br/><br/>

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
